Scalar Items in Embedded Position: {A}nother Experimental Approach

### 2012-05-21 text/paper/paper.tex
K2 paper sec com

\documentclass[fleqn,reqno,10pt]{article}

@@

In reaction to this situation, we therefore studied a different mode
of visual presentation: subjects were presented with pictures that
were partly covered and could incrementally be uncovered at the
subjects' request; for each ((partially) covered) picture, subjects
had to decide whether they could already give a truth-value judgement
or needed more information.\dn{mention who else does this} This way we
obtained behavioral data that is both indicative of the reading
subjects assumed and independent of the complexity of the visual
stimulus. At the same time, we hypothesized that the incremental
nature of this task would shed light on the preferences over readings,
because the temporal distribution of truth-value judgments would give
away which reading subjects were waiting to evaluate, so to speak.

To test whether our method is indeed suitable to detect interpretation
preferences, we included ambiguous test items like
(\ref{bsp:target-related-filler}) which are known to preferentially
receive the late-closure reading in
(\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
attested early-closure reading (\ref{bsp:target-related-filler-EC}).

@@

 with syntactically ambiguous
sentences whose interpretation preferences have been frequently
attested empirically.\dn{insert references to literature on EC-LC
  processing}

 Moreover,
since it is often argued (see Section~\ref{sec:theories-predictions})
that intonational stress on an embedded scalar item can favor a local
reading we presented sentence auditorily and manipulated stress
accordingly. The design of our studies is detailed in Section XYZ.

>>>>

\documentclass[fleqn,reqno,10pt,draft]{article}

@@

In reaction to this situation, we therefore studied a different mode
of visual presentation: subjects were presented with pictures that
were partly covered and could incrementally be uncovered at the
subjects' request; for each ((partially) covered) picture, subjects
had to decide whether they could already give a truth-value judgement
or needed more information.\dn{mention who else does this} This way we
obtained behavioral data that is both indicative of the reading
subjects assumed and independent of the complexity of the visual
stimulus. At the same time, we hypothesized that the incremental
nature of this task would shed light on the preferences over readings,
because the temporal distribution of truth-value judgments would give
away which reading subjects were waiting to evaluate, so to speak. To
test whether our method is indeed suitable to detect interpretation
preferences, we included ambiguous test items like
(\ref{bsp:target-related-filler}) which are known to preferentially
receive the late-closure reading in
(\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
attested early-closure reading
(\ref{bsp:target-related-filler-EC}).\dn{insert references to
  literature on EC-LC processing}

@@

\noindent Finally, since it is often argued (see
Section~\ref{sec:theories-predictions}) that intonational stress on an
embedded scalar item can favor a local reading we presented sentence
auditorily and manipulated stress accordingly. The design of our
studies is detailed in Section XYZ.
